\documentclass[10pt]{article}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{hyperref}

\setlength{\textheight}{9in} \setlength{\topmargin}{-.5in}
\setlength{\textwidth}{6.5in} \setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}

\title{Syllabus - COMP 325 - Organization of Programming Languages}
\author{  }
\date{Fall 2013}

\begin{document}
\maketitle

\section{Logistics}
\begin{itemize}
\item \textbf{Where: } Center for Science and Business, Room 303
\item \textbf{When: } MTWF,  9-9:50am
\item \textbf{Instructor :} James \textit{Logan} Mayfield
\begin{itemize}
\item \textit{Office: } Center for Science and Business, Room 344
\item \textit{Phone: } 309-457-2200
\item \textit{Email: } lmayfield at MONMOUTHCOLLEGE dot EDU
\item \textit{Office Hours: } By Appointment
\end{itemize}
\item \textbf{Credits: } 1 course credit
\end{itemize}
\emph{Note: Parts of this Syllabus are subject to change based on specific class needs.}

\section{Text}
%insert text #1
Krishnamurthi, Shriram. \textit{Programming Languages Application and Interpretation}. Second Edition. Creative Commons. 2012. 
\begin{itemize}
\item Main Site: \url{http://www.cs.brown.edu/~sk/Publications/Books/ProgLangs/2007-04-26/}
\item Book (HTML): \url{http://cs.brown.edu/courses/cs173/2012/book/}
\end{itemize}

%insert text #2 

\section{Programming Language and Environment}

We'll be using the \textit{Racket} programming language and DrRacket development environment in this course. The College lab computers are already loaded with the latest version of the DrRacket programming environment.    
\begin{itemize}
\item \url{http://www.racket-lang.org}
\end{itemize}

\section{Description and Content}
This course is an exploration of modern programming languages through the study and implementation of  interpreters for key language features.  By implementing small languages with common PL features, students expand their skill set with both practical and theoretical knowledge.  To understand programming languages is to understand programming and computation as a whole.  A programming language is how we describe a computational process and study of the languages themselves helps to shed light on the inner workings of a computation.
In addition to implementing some key programming language features, students will also experiment with modern, working programming languages which utilize these features.   

\subsection{Content}

This course will, for the most part, follow the text.  Topics to be covered will include:
\begin{itemize}
\item Language Design and Implementation
\item Identifiers 
\item Functions
\item First-Class Functions
\item Mutation
\item Recursion 
\item Objects
\item Garbage Collection
\item Static Types
\end{itemize}


\section{Expectations and Policies}
The expectations for students in this course are not at all unreasonable.  To avoid any confusion, they are listed here.  These aren't necessarily rules but rather guidelines for how you should conduct yourself in this class.  Strict rules will result from these expectations and will be covered later.
\begin{itemize}
\item Be respectful of others.  Don't create unnecessary distractions.  Turn cell phones off, on silent or leave them in the dorm.  Class time is not the time for checking email, surfing the web and IMing.  \textit{Come to class ready and interested in learning and if you're not, don't behave in such a way that prevents others from doing so.}
\item You're in college.  College is meant to provide an education.  Therefore, you are, for all intents and purposes, a \textit{professional student}.  Your work should reflect a solid level of professionalism and be neat and orderly.  Take the extra time to make it presentable.  Crumpled papers with various liquid stains on them are not presentable.  Think of the instructor as your boss and that the quality of your paycheck depends on the quality of the work.  \textit{You don't have to always love the work you do, but you should always do it to the best of your capabilities.}
\item Attending class is not by itself sufficient for learning the material.  You're expected to read the sections of the text as they are covered in class.  You are encouraged to go beyond the material.  Make use of available resources such as tutors and the high availability of your instructor.  \textit{Don't expect to get an A just by showing up and doing the least amount of work that you can.}
\end{itemize}

There are several strict policies that result from these expectations.  In the case of these items, they are rules and you are responsible for understanding and abiding by them.
\begin{itemize}
\item \textit{Late Assignments: }In general, late assignments will \textit{not} be accepted.  If you feel you have a justified reason for the assignment being late you may set up an appointment to meet with the instructor and plead your case.  Situations beyond your control are understandable and exceptions can and will be made.
\item \textit{Attendance: }You're an adult, you can choose to not come to class.  If you do miss/skip class \textit{you are still responsible for everything covered on that day}.  If you have no valid reason for missing class, do not expect the instructor to spend the time to re-present the class to you individually.
\item \textit{Participation: }  Cellphone usage in class is not allowed, this includes text messages.  Turn off the ringers or leave them at home.  Computer usage is limited to activities in support of the course.  This does not include IMs, Facebook, checking email, general web surfing, poker, fantasy sports leagues, forum trolling, mine sweeper, etc.  This behavior is rude and can be a real distraction to others.  Repeated failure to abide by this policy will have a negative effect on your grade.  
\item \textit{Quality of Work:} There are several minimal requirements that your assignments must meet.
\begin{itemize}
\item \textit{Staples - } Assignments that take up more than one page must be stapled.  Unstapled assignments will either be returned to you to be stabled ASAP or points will be deducted.  
\item \textit{Neatness - }  Make every attempt to make your work neat and orderly:  label problems, avoid excessive scratching out of mistakes (use pencil if you are prone to errors) and if you use spiral bound paper tear off the edges. 
\item \textit{Show Work - } Rarely are answers alone sufficient for full credit.  Show your work whenever prudent.  If you're unsure if work is needed, \textit{ask!}
\end{itemize}
\end{itemize}

\subsection{Collaboration}

In general, you are encouraged to make use of the resources available to you.  This means it is OK to seek help from a friend, tutor, instructor, internet, etc.  However, \textit{copying of answers and any act worthy of the label of ``cheating'' is never permissible!}  It is understandable that when you work with a partner or a group that the resultant product is often extremely similar.  This is acceptable but be prepared to be asked to defend your collaborations to the instructor.  \textit{You should always be able to reproduce an answer on your own, and if you cannot you likely \textbf{do not really known the material.}} 
\begin{itemize}
\item When assignments are meant to be done in groups, you will be directed to turn in one set of solutions per group.
\item All other assignments should represent your own work and effort.
\end{itemize}
All of the Monmouth College rules on academic dishonesty apply.  If you violate the rules be prepared to face the consequences of your actions.  

It is often more of a concern that you are not going to understand the material as well as you should because you rely too much on external sources.  It is up to you to be sure that you can produce the same work on your own when called upon to do so.  


\section{Grades}

This courses adheres to the Mathematics and Computer Science grade scale.  Assignments and final grades will not be curved except when deemed necessary by the instruction.  Percentage grades translate to letter grades as follows:
\newline
\begin{small}
\begin{tabular}{lc}
94-100 & A \\
90-93 & A- \\
88-89 & B+ \\
82-87 & B \\
79-81 & B- \\
76-78 & C+ \\
70-75 & C \\
67-69 & C- \\
64-66 & D+ \\
58-63 & D \\
55-57 & D- \\
0-54 & F 
\end{tabular}
\end{small}
\newline
You are always welcome to challenge a grade that you feel is unfair or calculated incorrectly.  Mistakes made in your favor will never be corrected to lower your grade.  Mistakes made not in your favor will be corrected.  \textit{Basically, after the initial grading your score can only go up as the result of a challenge.}

\subsection{Grade Weights}
Your final grade is based on a weighted average of particular assignment categories.  You should be able to estimate your current grade based on your scores and these weights.  You may always visit the instructor \textit{outside of class time} to discuss your current standing.  
\begin{itemize}
\item Homework 15\%
\item Paper + Presentation 20\%
\item Final 15\%
\item Midterm 10\%
\item Quizzes 30\%
\item Participation 10\%
% add more if needed
\end{itemize} 

\subsection{Workload}
% number of/details on midterms, finals, project, homeworks, quizes, etc

\begin{itemize}
\item 5 Homework Assignments
\item 1 Paper with Presentation
\item 1 Final
\item 1 Midterm
\item 5 Quizzes
\end{itemize}

\subsection{Course Engagement Expectations}

The weekly workload for this course will vary by student but on average should be about 11.5 hours per week.  The follow tables provides a rough estimate of the distribution of this time over different course components for a 15 week semester. 
\begin{center}
\begin{tabular}{|l|l|l|}
\hline
Lectures+Final &           & 3 hours/week \\ 
Homework & 30 hours        & 2 hours/week \\
Exam Study Time & 8 hours  & 0.5 hours/week \\ 
Quiz Study Time & 10 hours & 0.6 hours/week \\
Project & 24 hours         & 1.6 hours/week \\
Exercises &                & 2.3 hours/week \\
Reading+Unstructured Study & & 1.5 hours/week \\
\hline
& & 11.5 hours/week \\ 
\hline
\end{tabular}
\end{center}


\subsubsection{Calendar}

The following calendar should give you a feel for how work is distributed throughout the semester.  Assignments and events are listed in the week they are due or when the occur. \textit{This calendar is subject to change based on the circumstances of the course.}

\begin{center}
\begin{tabular}{|c|c|r|}
\hline 
Week & Dates & Assignments \\
\hline
1 & 8/25 - 8/28 &  \\
\hline 
2 & 8/31 - 9/4 &   \\
\hline
3 & 9/7 - 9/11 &   \\
\hline
4 & 9/14 - 9/18 &   \\
\hline
5 & 9/21 - 9/25 &  \\
\hline
6 & 9/28 - 10/2 & \\
\hline
7 & 10/5 - 10/9  &  \\
\hline 
8 & 10/12 - 10/15 &  FALL BREAK (F) \\
\hline
9 & 10/21 - 10/23 & FALL BREAK (M,Tu) \\
\hline
10 & 10/26 - 10/30 &  \\
\hline
11 & 11/2 - 11/6 & \\
\hline
12 & 11/9 - 11/13 &  \\
\hline
13 & 11/16 - 11/20 & \\
\hline
14 & 11/23 - 11/24 &  THANKSGIVING BREAK (W-F).   \\
\hline
15 & 11/30 - 12/4 & \\ 
\hline
16 & 12/7 - 12/9 &   Reading Day (Th). \\
\hline
Final's Week & 12/12 (6:30-9:30pm) & Final Exam. \\ 
\hline
\end{tabular}
\end{center}


\end{document}